Signal Processing to Demodulate FM Radio

### 2020-12-17 doc/paper/paper.tex
adapt text for matlab

    \subsubsection{Decimation}
      The signal still has a sample rate of 1 MHz, which is an overkill for the application, since a channels' bandwith only ranges up to 100 kHz.
      Keeping in mind the Nyquist theorem, the sample rate therefore needs to be at least 200 kHz.
      Thus, the signal is decimated by an arbitrary factor of 4 % TODO: more? see Nyquist.. work this out in script
      , which still leaves a rate of x M/kHz.

    \subsubsection{Demodulation}
      Demodulation is done by normalizing the signal amplitude to one.
      A FIR filter is used as a differentiator.
      Envelope detection is omitted for now, for simplicity and because of the mentioned effects in section \ref{demod_mono}.
    \subsubsection{Verification}
      Verification of correct functionality is only done subjectively, by listening to the demodulated audio signal via the PCs' soundcard.
      The OE3 stations' signal can be heard clearly.

>>>>

    \subsubsection{Decimation}
      The signal still has a sample rate of 1 MHz at this point.
      Keeping in mind the Nyquist theorem, and a single channels' bandwith of only up to 100 kHz, the sample rate therefore needs to be at least 200 kHz.
      However, the final hardware implementation is targeting an FPGA, where processing of samples at 1 MHz is easily achievable. Therefore, a decimation is not done at this point.
    \subsubsection{Demodulation}
      Demodulation is done by normalizing the signal amplitude to one.
      A FIR filter is used as a differentiator.
      Envelope detection is omitted for now, for simplicity and because of the mentioned effects in section \ref{demod_mono}.
    \subsubsection{Verification}
      Verification of correct functionality is only done subjectively, by listening to the demodulated audio signal via the PCs' soundcard.
      The OE3 stations' signal can be heard clearly.
